### 2015-02-03 abstract.tex
Adding old intro and old figures

%2. Related work:
%Update references with the work Torsten pointed out and the recent surface reconstruction survey that I mentioned. 
%Cite additional work that talks about the benefits of non-Cartsian lattices (in volume rendering, flow simulation etc.). 
There are a couple of works that deal with solving Poisson?s equation on non-Cartesian lattices. Please see the attached version of my paper.

3. Preliminaries:
Move sections 3.3.1 and 3.3.2 to section 6. Introduce 3.4 earlier.

4. Approach:
Expand 4.3 into a new section ? section 5. Move Table 1 to section 6.

5. Solving Poisson?s Equation.
This section spells out the details of the filtering methodology for solving Poisson?s equation. I will work on this part. The aim would be to condense the material so that it blends well with the rest of the paper.

6. Results and Discussion.
Start by introducing the specific lattices, basis functions, filters used for the experiments (3.3.1, 3.3.2 and table 1 should come here). Additionally, need a subsection here that derives the filter weights for CC and BCC. The rest of the section shows the comparative surface reconstruction experimental results + discussion.

7. Conclusion.
Usual mumbo jumbo.

>>>>

%2. Related work:
%Update references with the work Torsten pointed out and the recent surface reconstruction survey that I mentioned. 
%Cite additional work that talks about the benefits of non-Cartsian lattices (in volume rendering, flow simulation etc.). 
%There are a couple of works that deal with solving Poisson?s equation on non-Cartesian lattices. Please see the attached version of my paper.

%3. Preliminaries:
%Move sections 3.3.1 and 3.3.2 to section 6. Introduce 3.4 earlier.

%4. Approach:
%Expand 4.3 into a new section ? section 5. Move Table 1 to section 6.

%5. Solving Poisson?s Equation.
%This section spells out the details of the filtering methodology for solving Poisson?s equation. I will work on this part. The aim would be to condense the material so that it blends well with the rest of the paper.

%6. Results and Discussion.
%Start by introducing the specific lattices, basis functions, filters used for the experiments (3.3.1, 3.3.2 and table 1 should come here). Additionally, need a subsection here that derives the filter weights for CC and BCC. The rest of the section shows the comparative surface reconstruction experimental results + discussion.

%7. Conclusion.
%Usual mumbo jumbo.
